---
title: "Spatial and Temporal Coverage, Nash vs Baseline comparison"
author: "Quentin Goss `quentingoss0323@floridapoly.edu`"
output:
    html_document:
        df_print: paged
---

```{r include=FALSE}
# knitr::opts_chunk$set(echo=FALSE)
```


```{r message=FALSE, warning=FALSE}
library('tidyverse')
```

### Introduction
This is the first inspection of the Nash algorithm compared to the baseline algorithm for the *Spatial and Temporal Coverage Paper*.

##### Simulation Setup
**Parameter** | **Value** | **Description**
--------------+-----------+----------------
map           | london-seg4 | A SUMO SN of a portion of London, UK. Approximately $8000m * 6100m$ in size.
point.spawn   | $(1534.51,1148.80)$ | The $(x,y)$ point that marks the center of vehicle start locations.
point.sink    | $(7009.58,5560.75)$ | The $(x,y)$ point that marks the center of vehicle end locations.
radius.spawn.sink | 250 | The distance in meters from the start/end points that a start/end may exist. *Note: This is a square radius.*
targets       | 4 | The number of targets.
veh.total     | 100 | The number of vehicles that will exist in the entire simulation.
veh.exists.max| 100 | The number of vehicles that can exist at any point in time during the simulation.
nash.R        | 500 | Reward $R$ used by the Nas hAssigner to assign vehicle trajectories
nash.tau      | 1   | $\tau$ used by the Nash Assigner to assign vehicle trajectories

*Additional Notes:* In this experiment, we assign targets with the Nash Assigner only once.


##### Data Description
**Column**           | **Paper Notation** | **Description**
---------------------+--------------------+----------------
id                   | $i$                | Vehicle ID
source               | $s_i$              | The node ID  where the vehicle starts
destination          | $d_i$              | The node ID  where the vehicle ends
shortest.path.length | $s_i d_i$          | The weight of the shortest path  in seconds.  Measured by $\frac{l}{s}$ where $l$ is length in meters and $s$ is speed in meters/second.
diversion.path.length| $s_i T_k d_i$      | The weight of the diverion path  in seconds.
sample.time          | $t$                | Simulation time  in seconds where $t \in \mathbb{Z}_0^+$
sample.time.diff     | $t_{ik}-\overline{t_{ik}}$ |Time since the last sample at the reward 
target.id            | $T_k$              | The target ID.
utility              | $u(v_n,T_k) = R(1 - e^{-\frac{t_{ik}-\overline{t_{ik}}}{\tau}})-(|s_i T_k d_i| - |s_i d_i|)$ | Utility determined from the equation in the paper.    

### Helper Functions

Experiment Settings
```{r}
reward = 500
tau = 1
```


Read Vehicle .CSV function
```{r}
read.vehicle.csv <- function(file){
    data <-  read.csv(
        file=file,
        header=TRUE,
        sep=',',
        colClasses=c(
            'id' = 'character',
            'source' = 'character',
            'destination' = 'character',
            'shortest.path.length' = 'double',
            'diversion.path.length' = 'double',
            'sample.time' = 'double',
            'sample.time.diff' = 'double',
            'target.id' = 'character'
            )
        )
    return(as_tibble(data))
}
```

Mutate Utility Column Function
```{r}
mutate.utility <- function(veh.data) {
    veh.data <- veh.data %>%
        mutate(utility = reward * (1 - exp(-(sample.time.diff/tau))) - (abs(diversion.path.length) - abs(shortest.path.length)))
    return(veh.data)
}
```



### Baseline Data
```{r}
baseline.dir <- "./baseline/"
baseline.veh.csv <- paste0(baseline.dir,'vehicles.csv')
```

Data is loaded from CSV

```{r}
baseline.veh <- read.vehicle.csv(baseline.veh.csv)
```

Calculate the Utility
```{r}
baseline.veh <- mutate.utility(baseline.veh)
baseline.veh
```

Summary Statistics
```{r}
summary(baseline.veh)
```


### Nash Data
```{r}
nash.dir <- "./nash/"
nash.veh.csv <- paste0(nash.dir,"vehicles.csv")
```

Data Loaded from CSV
```{r}
nash.veh <- read.vehicle.csv(nash.veh.csv)
```

Calculate the Utility
```{r}
nash.veh <- mutate.utility(nash.veh)
nash.veh
```

Summary Statistics
```{r}
summary(nash.veh)
```

### Comparative Statistics

```{r warning=FALSE}
ggplot() +
    labs(title="Nash Vs Baseline", x = "Utility", y = "Sample Time Difference", color = "Method") +
    scale_color_manual(labels = c("Baseline","Nash"), values = c("red","blue")) +
    theme_bw() +
    geom_point(aes(x = baseline.veh$utility, y = baseline.veh$sample.time.diff, color = "red")) +
    geom_point(aes(x = nash.veh$utility, y = nash.veh$sample.time.diff, color = "blue"))
```

